{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Predictions for BHBH, BHNS and NSNS binaries in LISA

### 2021-09-28 paper/tex/sections/appendix.tex
random changes

>>>>

\begin{sidewaystable}
    \centering
    \begin{tabular}{c|ccccccccc|ccccccccc}
        \hline
        \multirow{3}{*}{Model} & \multicolumn{9}{c|}{4-year Mission} & \multicolumn{9}{c}{10-year Mission} \\
        \cline{2-9} \cline{10-19}
        & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c|}{Distinguishable} & \multicolumn{3}{c|}{$\Delta \mathcal{M}_c / \mathcal{M}_c < 0.1$} & \multicolumn{3}{c|}{$\sigma_\theta < 0.1 \unit{deg}$} & \multicolumn{3}{c}{Distinguishable}  \\
        \cline{2-9} \cline{10-19}
        & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} & \scriptsize{BHBH} & \scriptsize{BHNS} & \scriptsize{NSNS} \\
        \hline
        A & 0.15 & 0.11 & 0.68 & 0.23 & 0.15 & 0.65 & 0.29 & 0.24 & 0.61 & 0.12 & 0.10 & 0.59 & 0.18 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
B & 0.15 & 0.10 & 0.68 & 0.22 & 0.16 & 0.66 & 0.31 & 0.23 & 0.48 & 0.13 & 0.10 & 0.59 & 0.17 & 0.13 & 0.55 & 0.24 & 0.20 & 0.48 \\
C & 0.15 & 0.10 & 0.69 & 0.20 & 0.14 & 0.68 & 0.29 & 0.24 & 0.49 & 0.13 & 0.10 & 0.59 & 0.16 & 0.12 & 0.58 & 0.24 & 0.20 & 0.49 \\
D & 0.18 & 0.09 & 0.64 & 0.21 & 0.13 & 0.65 & 0.31 & 0.24 & 0.44 & 0.16 & 0.08 & 0.54 & 0.17 & 0.11 & 0.53 & 0.25 & 0.20 & 0.47 \\
E & 0.15 & 0.12 & 0.70 & 0.14 & 0.15 & 0.76 & 0.22 & 0.25 & 0.76 & 0.12 & 0.10 & 0.61 & 0.11 & 0.14 & 0.67 & 0.17 & 0.22 & 0.74 \\
F & 0.19 & 0.09 & 0.63 & 0.08 & 0.22 & 0.91 & 0.04 & 0.35 & 0.96 & 0.16 & 0.07 & 0.53 & 0.07 & 0.24 & 0.86 & 0.04 & 0.36 & 0.96 \\
G & 0.15 & 0.10 & 0.68 & 0.17 & 0.17 & 0.75 & 0.27 & 0.24 & 0.55 & 0.13 & 0.09 & 0.59 & 0.14 & 0.14 & 0.66 & 0.22 & 0.20 & 0.57 \\
H & 0.14 & 0.11 & 0.69 & 0.19 & 0.20 & 0.70 & 0.32 & 0.24 & 0.37 & 0.12 & 0.09 & 0.59 & 0.16 & 0.18 & 0.60 & 0.26 & 0.20 & 0.40 \\
I & 0.14 & 0.10 & 0.69 & 0.24 & 0.16 & 0.65 & 0.28 & 0.24 & 0.64 & 0.12 & 0.09 & 0.60 & 0.18 & 0.13 & 0.54 & 0.22 & 0.19 & 0.63 \\
J & 0.14 & 0.11 & 0.70 & 0.17 & 0.16 & 0.75 & 0.29 & 0.24 & 0.49 & 0.12 & 0.10 & 0.60 & 0.13 & 0.14 & 0.67 & 0.23 & 0.20 & 0.51 \\
K & 0.19 & 0.08 & 0.64 & 0.25 & 0.15 & 0.63 & 0.25 & 0.24 & 0.67 & 0.16 & 0.08 & 0.53 & 0.18 & 0.12 & 0.53 & 0.19 & 0.19 & 0.63 \\
L & 0.18 & 0.08 & 0.63 & 0.22 & 0.15 & 0.68 & 0.27 & 0.24 & 0.66 & 0.16 & 0.08 & 0.53 & 0.17 & 0.12 & 0.57 & 0.21 & 0.21 & 0.67 \\
M & 0.14 & 0.13 & 0.72 & 0.23 & 0.16 & 0.64 & 0.28 & 0.24 & 0.59 & 0.12 & 0.11 & 0.62 & 0.19 & 0.13 & 0.53 & 0.23 & 0.20 & 0.60 \\
N & 0.16 & 0.10 & 0.66 & 0.22 & 0.14 & 0.66 & 0.28 & 0.23 & 0.61 & 0.14 & 0.09 & 0.57 & 0.18 & 0.13 & 0.55 & 0.21 & 0.19 & 0.60 \\
O & 0.15 & 0.11 & 0.69 & 0.23 & 0.15 & 0.65 & 0.28 & 0.24 & 0.61 & 0.13 & 0.10 & 0.59 & 0.18 & 0.12 & 0.54 & 0.22 & 0.19 & 0.61 \\
P & 0.19 & 0.09 & 0.64 & 0.24 & 0.14 & 0.64 & 0.27 & 0.22 & 0.61 & 0.15 & 0.08 & 0.53 & 0.19 & 0.12 & 0.53 & 0.22 & 0.19 & 0.60 \\
Q & 0.18 & 0.09 & 0.64 & 0.26 & 0.15 & 0.60 & 0.29 & 0.23 & 0.57 & 0.17 & 0.08 & 0.54 & 0.20 & 0.12 & 0.49 & 0.22 & 0.19 & 0.56 \\
R & 0.15 & 0.10 & 0.68 & 0.24 & 0.15 & 0.63 & 0.27 & 0.23 & 0.60 & 0.12 & 0.10 & 0.59 & 0.19 & 0.12 & 0.50 & 0.21 & 0.18 & 0.59 \\
S & 0.18 & 0.08 & 0.65 & 0.20 & 0.13 & 0.68 & 0.23 & 0.22 & 0.71 & 0.16 & 0.08 & 0.54 & 0.17 & 0.12 & 0.57 & 0.18 & 0.19 & 0.70 \\
T & 0.16 & 0.09 & 0.70 & 0.23 & 0.15 & 0.62 & 0.33 & 0.25 & 0.43 & 0.13 & 0.08 & 0.60 & 0.18 & 0.12 & 0.50 & 0.26 & 0.20 & 0.45 \\
        \hline
    \end{tabular}
    \caption{A table}
\end{sidewaystable}
